PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-04 qfenv_paper/qf_environment.tex
Sections 1-2.5 Edited.
Continue editing edge effects section

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}

@@

%Section `ing
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our sample construction, and galaxy environment measurements. In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples. In Section \ref{sec:qf_const} we compare the quiescent fraction evolution for high and low density environments and discuss implications of the results on quenching mechanisms. In Section \ref{sec:summary} we summarize our results.

@@

\section{Sample Selection} \label{sec:sample}
In order to quantify the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.

@@

\subsection{PRIMUS} \label{sec:primus}
For our sample at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

Finally, from the spectroscopic redshift and broad wavelength photometry we use \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies. \texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters beyond the scope of this paper. For details we refer readers to Section 4.1 and Appendix A. of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

\subsection{SDSS-GALEX} \label{sec:sdss}
For our low redshift sample, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further narrow down the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This SDSS-{\em GALEX} sample contains $167,727$ galaxies.

Using the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, we obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies. For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude. These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}. As we did with the PRIMUS data above, we use \texttt{iSEDfit} with the above observed photometry to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the background subtraction improvements presented in \cite{Blanton:2011aa} and are single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a constant mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.

\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}

Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs. For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample. We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}. Given that our ultimate interest is in deriving the SMFs and QFs from our sample, we impose stellar mass limits in order to derive a stellar mass complete galaxy sample.

Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (galaxies are classified into star-forming or quiescent in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

To derive the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.0375 < z < 0.145$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}). To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog. Furthermore, to derive a stellar mass complete sample, we impose a uniform stellar mass limit of $10^9.8 \; \mathcal{M}_{\odot}$, which is determined from the mass-to-light ratio completeness limit of the SDSS-{\em GALEX} sample within the imposed redshift limit.

With the stellar mass completeness limits above, we have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS. However since our sample is derived from two different surveys, we must account for the disparity in the redshift uncertainty. While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts. The differences in redshift uncertainties becomes especially important in environment classifications (environment measurements and classification is later discussed in Section \ref{sec:environment}). In order to have comparable contamination in environment classifications, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy in our sample, we compute its $\sigma_z$ by randomly sampling within three standard deviations of a normal distribution where the standard deviation is derived from the $z_{\rm{SDSS}-GALEX}$ of the galaxy, $\sigma = 0.005 (1+z_{\rm{SDSS}- GALEX})$

The absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) is plotted in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the portion of the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Then using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

@@

\subsection{Galaxy Environment} \label{sec:environment}
With the galaxy sample divided into quiescent and star-forming galaxies above, we now classify the galaxies into high and low density environments. In this section, we describe our method for measuring the environment for our galaxy sample. First, we define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales. For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and the PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so aperture height of $25 \; \rm{Mpc}/h$ accounts for both of these effects. Our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass. \cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale. When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
%Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
%Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
%galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}).

Using the fixed aperture environment definition, we now measure the environment for our galaxy sample. First, we construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal. In addition to providing a reasonable comparison of environment measurements for wide redshift range, it also seeks to construct an EDP that contains similar galaxy populations through the redshift range (i.e. accounts for the progenitor bias). As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density method, though it does not precisely account for the scatter in mass accretion or galaxy-galaxy mergers, it provides a reasonable means to compare galaxy populations over a wide range of cosmic time.

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{4}, 
Ken Wong\altaffilmark{3}, 
Guangtun Zhu\altaffilmark{3}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}

@@

\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements. After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples. In Section \ref{sec:qf_const}, we calculate the quiescent fraction and compare the evolution of the quiescent fraction between high and low density environments. In Section \ref{sec:discussion} we discuss the trends observed in the stellar mass function and quiescent fraction evolution and discuss implications of the results on quenching mechanisms. Finally in Section \ref{sec:summary} we summarize our results.

@@

\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

@@

\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$. The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

@@

Finally, from the spectroscopic redshift and broad wavelength photometry we use \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies. \texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A. of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}). We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies. For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude. These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}. As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.

@@

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.

\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}
From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample. We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}. More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}. Since we are ultimately interested in a mass complete galaxy sample to derive SMFs and QFs, next we impose stellar mass completeness limits to our galaxy sample.

Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

For the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.05 < z < 0.12$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}). To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog. Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio of the SDSS-{\rm GALEX} data within the imposed redshift limits. We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.

We now have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS data. Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty. While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts. In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a normal distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.

We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

@@

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.

For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25 \; \rm{Mpc}/h$ accounts for both of these effects. Our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass. \cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.

%When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
%Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
%Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
%galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}).

Before we measure the environment for our galaxy sample, we first construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal. In addition to providing a reasonable comparison of environment measurements for wide redshift range, it also seeks to construct an EDP that contains similar galaxy populations through the redshift range (i.e. accounts for the progenitor bias). As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density method, though it does not precisely account for the scatter in mass accretion or galaxy-galaxy mergers, it provides a reasonable means to compare galaxy populations over a wide range of cosmic time.

In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}). We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$. We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.75$. Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.75$.
